fGFPCA dynamic prediction (In-sample)

### 2022-11-21 f-GFPCA.Rmd
clean up figures

library(here)
library(tidyverse)
library(ggplot2)
library(fcr)
library(refund)
library(lme4)
set.seed(1025)
```

@@

```{r}
# Try on subjectw 1-4

clean_pred(1) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))

clean_pred(2) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))

clean_pred(3) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))

clean_pred(4) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))

```
- Subject 2

```{r}
# Try on subject 1
pred20 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 20, df_pred_unique, subj=2),
                     type = "up to 195") %>% 
  filter(bin>195)

pred40 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 40, df_pred_unique, subj=2),
                     type = "up to 395") %>%
  filter(bin>395)

pred60 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 60, df_pred_unique, subj=2),
                     type = "up to 595") %>%
  filter(bin>595)

clean_pred(1)
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))
```

- Subject 3

```{r}
# Try on subject 1
pred20 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 20, df_pred_unique, subj=3),
                     type = "up to 195") %>% 
  filter(bin>195)

pred40 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 40, df_pred_unique, subj=3),
                     type = "up to 395") %>%
  filter(bin>395)

pred60 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 60, df_pred_unique, subj=3),
                     type = "up to 595") %>%
  filter(bin>595)

df_pred_latent %>% filter(id==3 & sind_inx==bin) %>%
  select(bin, eta_i) %>% mutate(type="true") %>%
  add_row(pred20) %>%
  add_row(pred40) %>% 
  add_row(pred60) %>% 
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))
```
- Subject 4

```{r}
# Try on subject 1
pred20 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 20, df_pred_unique, subj=4),
                     type = "up to 195") %>% 
  filter(bin>195)

pred40 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 40, df_pred_unique, subj=4),
                     type = "up to 395") %>%
  filter(bin>395)

pred60 <- data.frame(bin = mid, 
                     eta_i = in_samp_dyn_pred(fpca_fit, 60, df_pred_unique, subj=4),
                     type = "up to 595") %>%
  filter(bin>595)

df_pred_latent %>% filter(id==4 & sind_inx==bin) %>%
  select(bin, eta_i) %>% mutate(type="true") %>%
  add_row(pred20) %>%
  add_row(pred40) %>% 
  add_row(pred60) %>% 
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))

>>>>

library(here)
library(tidyverse)
library(ggplot2)
library(fcr)
library(refund)
library(lme4)
library(ggpubr)
set.seed(1025)
```

@@

```{r}
# Try on subjects 1-4
ggarrange(
clean_pred(1) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))+
  labs(title = "Subject 1"),

clean_pred(2) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))+
  labs(title = "Subject 2"),

clean_pred(3) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))+
  labs(title = "Subject 3"),

clean_pred(4) %>%
  ggplot()+
  geom_line(aes(x=bin, y = eta_i, col=type))+
  labs(title = "Subject 4"), nrow=2, ncol=2, common.legend = T)
